\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-21 paper.qmd
Updated Figure 15

error_plot_pbmc <- ggplot(error_pbmc, 
                          aes(x = a1, 
                              y = MSE, 
                              colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_color_manual(values=c('#e41a1c','#377eb8','#4daf4a','#ff7f00',
                              '#984ea3','#999999','#a65628','#f781bf')) +
  ylab("MSE") +
  xlab(expression(a[1])) + 
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7, angle = 90),
        axis.ticks.x = element_line(linewidth = 0.5),
        axis.ticks.y = element_line(linewidth = 0.5),
        legend.position = "none") #+
  # inset_element(p = pbmc_layouts, 
  #               left = 1.55, 
  #               bottom = 0.35, 
  #               right = 0, 
  #               top = 1)

@@

```{r}
#| fig-cap: "MSE from UMAP with diffferent (hyper-)parameter choices and tSNE with default (hyper-)parameter setting applied to PBMC3k dataset for different number of bins along the x-axis ($b_1$). Which is the most reasonable representation of the structures present in the PBMC3k data? The residual plot have a steep slope at the beginning, indicating that a smaller $b_1$ causes a larger amount of error. Then, the slope gradually declines or level off, indicating that a higher number of $b_1$ generates a smaller error. It was observed that for every $b_1$, the lowest error occurred with tSNE using the perplexity: $30$."
#| label: fig-pbmc-mse
#| fig-pos: H
#| out-height: 100%

>>>>

error_plot_pbmc <- ggplot(error_pbmc, 
                          aes(x = a1, 
                              y = log(MSE), 
                              colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_color_manual(values=c('#e41a1c','#377eb8','#4daf4a','#ff7f00',
                              '#984ea3','#999999','#a65628','#f781bf')) +
  ylab("log(MSE)") +
  xlab(expression(a[1])) + 
  theme(#aspect.ratio = 0.75,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7, angle = 90),
        axis.ticks.x = element_line(linewidth = 0.5),
        axis.ticks.y = element_line(linewidth = 0.5),
        legend.position = "none") #+
  # inset_element(p = pbmc_layouts, 
  #               left = 1.55, 
  #               bottom = 0.35, 
  #               right = 0, 
  #               top = 1)

@@

```{r}
#| fig-cap: "MSE from UMAP, tSNE, PHATE, PaCMAP, and TriMAP wwith diffferent (hyper-)parameter choices applied to PBMC3k dataset for different number of bin widths along the x-axis ($a_1$). Which is the most reasonable representation of the structures present in the PBMC3k data? The residual plot have a steep slope at the beginning, indicating that a smaller $a_1$ causes a smaller amount of error. Then, the slope gradually increases or level up, indicating that a higher number of $a_1$ generates a larger error. It was observed that for every $a_1$, the lowest error occurred with tSNE using the perplexity: $30$."
#| label: fig-pbmc-mse
#| fig-pos: H
#| out-height: 100%

### 2024-08-21 paper.tex
Removed unnecessary codes
Removed plots with q
Replot Figure 15
Updated Figure 15

\includegraphics[width=0.7\textwidth,height=\textheight]{paper_files/figure-pdf/fig-pbmc-mse-1.pdf}

@@

\caption{\label{fig-pbmc-mse}MSE from UMAP with diffferent
(hyper-)parameter choices and tSNE with default (hyper-)parameter
setting applied to PBMC3k dataset for different number of bins along the
x-axis (\(b_1\)). Which is the most reasonable representation of the
structures present in the PBMC3k data? The residual plot have a steep
slope at the beginning, indicating that a smaller \(b_1\) causes a
larger amount of error. Then, the slope gradually declines or level off,
indicating that a higher number of \(b_1\) generates a smaller error. It
was observed that for every \(b_1\), the lowest error occurred with tSNE
using the perplexity: \(30\).}

>>>>

\includegraphics[width=1\textwidth,height=1\textheight]{paper_files/figure-pdf/fig-pbmc-mse-1.pdf}

@@

\caption{\label{fig-pbmc-mse}MSE from UMAP, tSNE, PHATE, PaCMAP, and
TriMAP wwith diffferent (hyper-)parameter choices applied to PBMC3k
dataset for different number of bin widths along the x-axis (\(a_1\)).
Which is the most reasonable representation of the structures present in
the PBMC3k data? The residual plot have a steep slope at the beginning,
indicating that a smaller \(a_1\) causes a smaller amount of error.
Then, the slope gradually increases or level up, indicating that a
higher number of \(a_1\) generates a larger error. It was observed that
for every \(a_1\), the lowest error occurred with tSNE using the
perplexity: \(30\).}
